% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[katie-mcginley]{Katie McGinley}

\thinrule

\startblockquote
Frontend Developer
\stopblockquote

\thinrule

\placetable[none]{}
\starttable[|l|r|]
\HL
\NC Berlin, Germany
\NC katie@mcgnly.com
\NC\AR
\NC mcgnly.com
\NC @mcgnly
\NC\AR
\NC github.com/mcgnly
\NC 0049 176 3860 4667
\NC\AR
\HL
\stoptable

\subsection[work-experience]{Work Experience}

{\bf Frontend developer, relayr}

{\em December 2015-present}

\startitemize
\item
  member of core-products development team
\item
  reworked authorization and user-creation flow for core business
  platform
\item
  developed react-based UI components for team use in future products
\item
  migrated internal services to new backend architecture available after
  acquisition, including SDK
\item
  lead developer for notification service dashboard
\item
  frontend developer for batch-data download service
\item
  frontend developer for sensor data analysis using
\item
  lead developer for javascript SDK for notification service API
\item
  reworked javascript SDK for main product API
\stopitemize

\subsection[side-projects]{Side Projects}

\startitemize
\item
  \useURL[url1][https://github.com/mcgnly/volunqueer][][Volunqueer]\from[url1]:
  Platform based on react to match organizations with individuals
  wanting to do community service and volunteer within the LGBTQ
  community- as a volunteer, you can filter the suggestions based on
  your interests and the kind of work which you would like to do, and
  sign up for a weekly digest of new volunteer opportunities that match
  your interests. As an organization, you can post volunteer positions
  quickly, and match with volunteers. Winner of the 2017 Unicorns in
  Tech Hackathon. Available at: http://volunqueer.herokuapp.com
\item
  \useURL[url2][https://github.com/mcgnly/email-keyword][][AFP-Alert]\from[url2]:
  Amanda Palmer is an American musician who tours a lot, and has a
  tenency to do free concerts here and there with short notice given on
  Twitter. I created a tool to watch her twitter and send out an email
  alert when she mentions a chosen town, so that people who sign up for
  the service will know if she is thinking of coming to their area. Tool
  and website built with meteor, database to hold collections of emails
  and keywords on Mongo, hosted on AWS. Available at:
  http://afp-alert.mcgnly.com\crlf
\item
  \useURL[url3][https://github.com/mcgnly/mcgnly-home][][mcgnly.com]\from[url3]:
  The source code for my introduction website. My focus here was
  creating a concise overview of the projects I have worked on until
  now, a place to host my resume, and to learn concepts relating to
  accessability. Hosted on using Github-pages. Found at: www.mcgnly.com
\item
  \useURL[url4][https://github.com/mcgnly/basic-redux][][Basic
  Redux]\from[url4]: A teaching tool for the basics of development in
  react and how to incorporate redux, to explain the basics and make it
  easy to interact with different elements to better understand how they
  fit together. Built using create-react-app, redux, less, and gulp.
\item
  \useURL[url5][https://github.com/mcgnly/alexa-iss][][Space Station
  Locator]\from[url5]: One of a series of apps built for Amazon Alexa.
  Takes the current time and returns the point on Earth over which the
  International Space Station is at this very second. Built using Node
  and Amazon Lambda. Available at:
  \useURL[url6][https://www.amazon.com/mcgnly-Space-Station/dp/B01MZ2ONRB/ref=sr_1_2?s=digital-skills&ie=UTF8&qid=1486298736&sr=1-2&keywords=mcgnly][][the
  Alexa app store]\from[url6]
\item
  \useURL[url7][https://github.com/mcgnly/million-monkeys][][Million
  Monkeys]\from[url7]: A python command-line app that, when given a
  particular string, will replicate it using randomly generated
  characters, and count the number of repetitions it takes to recreate
  the given word or phrase.
\stopitemize

\subsection[education]{Education}

\startitemize[packed]
\item
  Bachelor of Science in Mechanical Engineering, University of
  Pittsburgh
\stopitemize

\subsection[technical-skills]{Technical Skills}

{\bf Developer-related:}

\startitemize[packed]
\item
  react\crlf
\item
  redux\crlf
\item
  angular\crlf
\item
  webpack\crlf
\item
  gulp\crlf
\item
  javascript ES6 and ES7\crlf
\item
  CSS and LESS\crlf
\item
  html\crlf
\item
  unit testing with mocha, chai, and Jest\crlf
\item
  CI using Jenkins\crlf
\stopitemize

{\bf Non-developer-related:}

\startitemize[packed]
\item
  3d mechanical design using Solidworks, OnShape, and Rhino\crlf
\item
  ruggedized design for 2-part injection molding\crlf
\item
  design for IP-67 water and dust ingress protection\crlf
\item
  six-sigma green-belt certification\crlf
\item
  German, French, Italian\crlf
\stopitemize

\stoptext
